---
title: "Alignment graphs and tables"
author: "Rachel Ancar"
date: "11/01/2018"
output:
  html_document:
    code_folding: hide
    toc: yes
    toc_float: yes
  pdf_document:
    toc: yes
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(message = FALSE)
```


```{r, message = F, warning = F}

library(tidyverse)
library(readr)
library(dplyr)
library(ggplot2)
library(stringr)
library(cowplot)
library(RColorBrewer)
library(purrr)
library(shiny)
library(DT)

```


#Experiment 1: overview of counts and normalized counts for each type of RNA species


##Table of umi-corrected reads

```{r, warning = F}

data_dir = "~/Dropbox (Hesselberth Lab)/Rachel_data/EndoU_project/all_RNA_bg/exp_1"
data_files = list.files(data_dir, full.names = T)

read_file <- function(x) {
  df <- readr::read_tsv(x, col_names = c("chrom", "start", "end", "count", "normalized"))
  df$name <- basename(x)
  df
}

all_table <- purrr::map_df(data_files, read_file) %>%
  mutate(name = str_replace(name, ".normalized.bg", "")) %>%
  separate(chrom, into = c('RNA_type', 'extra'), sep = '\\|') %>% 
  dplyr::select(-extra) %>%
  separate(name, into = c('cell', 'virus', 'time'), sep = '_') 

all_reads <- all_table %>%
  group_by(cell, virus, time) %>%
  mutate(total_umi_reads = sum(count)) %>%
  select(cell, virus, time, total_umi_reads) %>%
  unique()

mhv_reads <- all_table %>%
  filter(RNA_type == "mhv") %>%
  group_by(cell, virus, time) %>%
  mutate(mhv_umi_reads = sum(count)) %>%
  select(cell, virus, time, mhv_umi_reads) %>%
  unique()

alignments_table <- left_join(all_reads, mhv_reads)

mRNA_reads <- all_table %>%
  filter(RNA_type == "mRNA") %>%
  group_by(cell, virus, time) %>%
  mutate(mRNA_umi_reads = sum(count)) %>%
  select(cell, virus, time, mRNA_umi_reads) %>%
  unique()

alignments_table <- left_join(alignments_table, mRNA_reads)

tRNA_reads <- all_table %>%
  filter(RNA_type == "tRNA") %>%
  group_by(cell, virus, time) %>%
  mutate(tRNA_umi_reads = sum(count)) %>%
  select(cell, virus, time, tRNA_umi_reads) %>%
  unique()

alignments_table <- left_join(alignments_table, tRNA_reads)

U6_reads <- all_table %>%
  filter(RNA_type == "U6") %>%
  group_by(cell, virus, time) %>%
  mutate(U6_umi_reads = sum(count)) %>%
  select(cell, virus, time, U6_umi_reads) %>%
  unique()

alignments_table <- left_join(alignments_table, U6_reads)

r5s_reads <- all_table %>%
  filter(RNA_type == "r5s") %>%
  group_by(cell, virus, time) %>%
  mutate(r5s_umi_reads = sum(count)) %>%
  select(cell, virus, time, r5s_umi_reads) %>%
  unique()

alignments_table <- left_join(alignments_table, r5s_reads)

r5.8s_reads <- all_table %>%
  filter(RNA_type == "r5.8s") %>%
  group_by(cell, virus, time) %>%
  mutate(r5.8s_umi_reads = sum(count)) %>%
  select(cell, virus, time, r5.8s_umi_reads) %>%
  unique()

alignments_table <- left_join(alignments_table, r5.8s_reads)

r18s_reads <- all_table %>%
  filter(RNA_type == "r18s") %>%
  group_by(cell, virus, time) %>%
  mutate(r18s_umi_reads = sum(count)) %>%
  select(cell, virus, time, r18s_umi_reads) %>%
  unique()

alignments_table <- left_join(alignments_table, r18s_reads)

r28s_reads <- all_table %>%
  filter(RNA_type == "r28s") %>%
  group_by(cell, virus, time) %>%
  mutate(r28s_umi_reads = sum(count)) %>%
  select(cell, virus, time, r28s_umi_reads) %>%
  unique()

alignments_table <- left_join(alignments_table, r28s_reads)

datatable(alignments_table)


```

##Table and graphs of total and percent total umi-reads for each RNA species

```{r, warning = F}

percent_total <- function(x){
  percent_cdna <- x %>% 
  mutate_at(.fun = funs(percent = ./total_umi_reads * 100), .vars = 5:12)
  return(percent_cdna)
}

final_table <- percent_total(alignments_table)

datatable(final_table)


```

### MHV

```{r, warning = F}

MHVreads_graph <- final_table %>%
  ggplot(aes(x = cell , y = mhv_umi_reads)) + 
  scale_fill_brewer(palette = 'Set1') + 
  geom_bar(aes(fill = time), stat = "identity", position = 'dodge') +
  theme_cowplot() + 
  facet_grid( ~ virus) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(x="MHV (+) RNA", y="Umi corrected reads")
MHVreads_graph

MHVpercentreads_graph <- final_table %>%
  ggplot(aes(x = cell , y = mhv_umi_reads_percent)) + 
  scale_fill_brewer(palette = 'Set1') + 
  geom_bar(aes(fill = time), stat = "identity", position = 'dodge') +
  theme_cowplot() + 
  facet_grid( ~ virus) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(x="MHV (+) RNA", y="Percent umi corrected reads")
MHVpercentreads_graph

```

### mRNA 

```{r}

mRNAreads_graph <- final_table %>%
  ggplot(aes(x = cell , y = mRNA_umi_reads)) + 
  scale_fill_brewer(palette = 'Set1') + 
  geom_bar(aes(fill = time), stat = "identity", position = 'dodge') +
  theme_cowplot() + 
  facet_grid( ~ virus) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(x="mRNA", y="Umi corrected reads")
mRNAreads_graph

mRNApercentreads_graph <- final_table %>%
  ggplot(aes(x = cell , y = mRNA_umi_reads_percent)) + 
  scale_fill_brewer(palette = 'Set1') + 
  geom_bar(aes(fill = time), stat = "identity", position = 'dodge') +
  theme_cowplot() + 
  facet_grid( ~ virus) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(x="mRNA", y="Percent umi corrected reads")
mRNApercentreads_graph


```

#tRNAs

```{r}

tRNAreads_graph <- final_table %>%
  ggplot(aes(x = cell , y = tRNA_umi_reads)) + 
  scale_fill_brewer(palette = 'Set1') + 
  geom_bar(aes(fill = time), stat = "identity", position = 'dodge') +
  theme_cowplot() + 
  facet_grid( ~ virus) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(x="tRNA", y="Umi corrected reads")
tRNAreads_graph

tRNApercentreads_graph <- final_table %>%
  ggplot(aes(x = cell , y = tRNA_umi_reads_percent)) + 
  scale_fill_brewer(palette = 'Set1') + 
  geom_bar(aes(fill = time), stat = "identity", position = 'dodge') +
  theme_cowplot() + 
  facet_grid( ~ virus) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(x="tRNA", y="Percent umi corrected reads")
tRNApercentreads_graph


```

#U6

```{r}

U6reads_graph <- final_table %>%
  ggplot(aes(x = cell , y = U6_umi_reads)) + 
  scale_fill_brewer(palette = 'Set1') + 
  geom_bar(aes(fill = time), stat = "identity", position = 'dodge') +
  theme_cowplot() + 
  facet_grid( ~ virus) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(x="U6", y="Umi corrected reads")
U6reads_graph

U6percentreads_graph <- final_table %>%
  ggplot(aes(x = cell , y = U6_umi_reads_percent)) + 
  scale_fill_brewer(palette = 'Set1') + 
  geom_bar(aes(fill = time), stat = "identity", position = 'dodge') +
  theme_cowplot() + 
  facet_grid( ~ virus) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(x="U6", y="Percent umi corrected reads")
U6percentreads_graph


```

#5s rRNA

```{r}

r5sreads_graph <- final_table %>%
  ggplot(aes(x = cell , y = r5s_umi_reads)) + 
  scale_fill_brewer(palette = 'Set1') + 
  geom_bar(aes(fill = time), stat = "identity", position = 'dodge') +
  theme_cowplot() + 
  facet_grid( ~ virus) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(x="5s rRNA", y="Umi corrected reads")
r5sreads_graph

r5spercentreads_graph <- final_table %>%
  ggplot(aes(x = cell , y = r5s_umi_reads_percent)) + 
  scale_fill_brewer(palette = 'Set1') + 
  geom_bar(aes(fill = time), stat = "identity", position = 'dodge') +
  theme_cowplot() + 
  facet_grid( ~ virus) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(x="5s rRNA", y="Percent umi corrected reads")
r5spercentreads_graph


```

#18s rRNA

```{r}

r18sreads_graph <- final_table %>%
  ggplot(aes(x = cell , y = r18s_umi_reads)) + 
  scale_fill_brewer(palette = 'Set1') + 
  geom_bar(aes(fill = time), stat = "identity", position = 'dodge') +
  theme_cowplot() + 
  facet_grid( ~ virus) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(x="18s rRNA", y="Umi corrected reads")
r18sreads_graph

r18spercentreads_graph <- final_table %>%
  ggplot(aes(x = cell , y = r18s_umi_reads_percent)) + 
  scale_fill_brewer(palette = 'Set1') + 
  geom_bar(aes(fill = time), stat = "identity", position = 'dodge') +
  theme_cowplot() + 
  facet_grid( ~ virus) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(x="18s rRNA", y="Percent umi corrected reads")
r18spercentreads_graph

```

#5.8 rRNA

```{r}

r5.8sreads_graph <- final_table %>%
  ggplot(aes(x = cell , y = r5.8s_umi_reads)) + 
  scale_fill_brewer(palette = 'Set1') + 
  geom_bar(aes(fill = time), stat = "identity", position = 'dodge') +
  theme_cowplot() + 
  facet_grid( ~ virus) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(x="5.8s rRNA", y="Umi corrected reads")
r5.8sreads_graph

r5.8spercentreads_graph <- final_table %>%
  ggplot(aes(x = cell , y = r5.8s_umi_reads_percent)) + 
  scale_fill_brewer(palette = 'Set1') + 
  geom_bar(aes(fill = time), stat = "identity", position = 'dodge') +
  theme_cowplot() + 
  facet_grid( ~ virus) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(x="5.8s rRNA", y="Percent umi corrected reads")
r5.8spercentreads_graph

```

#28s rRNA

```{r}

r28sreads_graph <- final_table %>%
  ggplot(aes(x = cell , y = r28s_umi_reads)) + 
  scale_fill_brewer(palette = 'Set1') + 
  geom_bar(aes(fill = time), stat = "identity", position = 'dodge') +
  theme_cowplot() + 
  facet_grid( ~ virus) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(x="28s rRNA", y="Umi corrected reads")
r28sreads_graph

r28spercentreads_graph <- final_table %>%
  ggplot(aes(x = cell , y = r28s_umi_reads_percent)) + 
  scale_fill_brewer(palette = 'Set1') + 
  geom_bar(aes(fill = time), stat = "identity", position = 'dodge') +
  theme_cowplot() + 
  facet_grid( ~ virus) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(x="28s rRNA", y="Percent umi corrected reads")
r28spercentreads_graph


```

##Graphs of percent total umi-reads for all RNA subtypes by cell type


###B6

```{r, warning = F}

B6_graph <- final_table %>%
        filter(cell == "B6") %>%
        gather(RNA_type, percent_total_reads, 13:20) %>%
        separate(RNA_type, into = c('RNA_type'), sep = '_') %>%
        ggplot(aes(x = RNA_type , y = percent_total_reads)) + 
        scale_fill_brewer(palette = 'Set1') + 
        geom_bar(aes(fill = time), stat = "identity", position = 'dodge') +
        theme_cowplot() + 
        facet_grid( ~ virus) +
        theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 8)) +
        labs(x="B6 WT macrophages", y="Percent umi corrected reads")
B6_graph
          

```

### IFNAR KO

```{r, warning = F}

IFNAR_graph <- final_table %>%
        filter(cell == "IFNAR") %>%
        gather(RNA_type, percent_total_reads, 13:20) %>%
        separate(RNA_type, into = c('RNA_type'), sep = '_') %>%
        ggplot(aes(x = RNA_type , y = percent_total_reads)) + 
        scale_fill_brewer(palette = 'Set1') + 
        geom_bar(aes(fill = time), stat = "identity", position = 'dodge') +
        theme_cowplot() + 
        facet_grid( ~ virus) +
        theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 8)) +
        labs(x="B6 IFNAR KO macrophages", y="Percent umi corrected reads")
IFNAR_graph

```


### RNaseL KO

```{r, warning = F}

RNaseL_graph <- final_table %>%
        filter(cell == "RNaseL") %>%
        gather(RNA_type, percent_total_reads, 13:20) %>%
        separate(RNA_type, into = c('RNA_type'), sep = '_') %>%
        ggplot(aes(x = RNA_type , y = percent_total_reads)) + 
        scale_fill_brewer(palette = 'Set1') + 
        geom_bar(aes(fill = time), stat = "identity", position = 'dodge') +
        theme_cowplot() + 
        facet_grid( ~ virus) +
        theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 8)) +
        labs(x="B6 RNaseL KO macrophages", y="Percent umi corrected reads")
RNaseL_graph

```

#Experiment 2: overview of counts and normalized counts for each type of RNA species


##Table of umi-corrected reads

```{r, warning = F}

data_dir = "~/Dropbox (Hesselberth Lab)/Rachel_data/EndoU_project/all_RNA_bg/exp_2"
data_files = list.files(data_dir, full.names = T)

read_file <- function(x) {
  df <- readr::read_tsv(x, col_names = c("chrom", "start", "end", "count", "normalized"))
  df$name <- basename(x)
  df
}

all_table <- purrr::map_df(data_files, read_file) %>%
  mutate(name = str_replace(name, ".normalized.bg", "")) %>%
  separate(chrom, into = c('RNA_type', 'extra'), sep = '\\|') %>% 
  dplyr::select(-extra) %>%
  separate(name, into = c('cell', 'virus', 'time'), sep = '_') 

all_reads <- all_table %>%
  group_by(cell, virus, time) %>%
  mutate(total_umi_reads = sum(count)) %>%
  select(cell, virus, time, total_umi_reads) %>%
  unique()

mhv_reads <- all_table %>%
  filter(RNA_type == "mhv") %>%
  group_by(cell, virus, time) %>%
  mutate(mhv_umi_reads = sum(count)) %>%
  select(cell, virus, time, mhv_umi_reads) %>%
  unique()

alignments_table <- left_join(all_reads, mhv_reads)

mRNA_reads <- all_table %>%
  filter(RNA_type == "mRNA") %>%
  group_by(cell, virus, time) %>%
  mutate(mRNA_umi_reads = sum(count)) %>%
  select(cell, virus, time, mRNA_umi_reads) %>%
  unique()

alignments_table <- left_join(alignments_table, mRNA_reads)

r5.8s_reads <- all_table %>%
  filter(RNA_type == "r5.8s") %>%
  group_by(cell, virus, time) %>%
  mutate(r5.8s_umi_reads = sum(count)) %>%
  select(cell, virus, time, r5.8s_umi_reads) %>%
  unique()

alignments_table <- left_join(alignments_table, r5.8s_reads)

r5s_reads <- all_table %>%
  filter(RNA_type == "r5s") %>%
  group_by(cell, virus, time) %>%
  mutate(r5s_umi_reads = sum(count)) %>%
  select(cell, virus, time, r5s_umi_reads) %>%
  unique()

alignments_table <- left_join(alignments_table, r5s_reads)

r18s_reads <- all_table %>%
  filter(RNA_type == "r18s") %>%
  group_by(cell, virus, time) %>%
  mutate(r18s_umi_reads = sum(count)) %>%
  select(cell, virus, time, r18s_umi_reads) %>%
  unique()

alignments_table <- left_join(alignments_table, r18s_reads)

r28s_reads <- all_table %>%
  filter(RNA_type == "r28s") %>%
  group_by(cell, virus, time) %>%
  mutate(r28s_umi_reads = sum(count)) %>%
  select(cell, virus, time, r28s_umi_reads) %>%
  unique()

alignments_table <- left_join(alignments_table, r28s_reads) %>%
  mutate_all(funs(replace(., is.na(.), 0)))

datatable(alignments_table)


```

##Table and graphs of total and percent total umi-reads for each RNA species

```{r, warning = F}

percent_total <- function(x){
  percent_cdna <- x %>% 
  mutate_at(.fun = funs(percent = ./total_umi_reads * 100), .vars = 5:10)
  return(percent_cdna)
}

final_table <- percent_total(alignments_table)

datatable(final_table)


```

### MHV

```{r, warning = F}

MHVreads_graph <- final_table %>%
  ggplot(aes(x = cell , y = mhv_umi_reads)) + 
  scale_fill_brewer(palette = 'Set1') + 
  geom_bar(aes(fill = time), stat = "identity", position = 'dodge') +
  theme_cowplot() + 
  facet_grid( ~ virus) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(x="MHV (+) RNA", y="Umi corrected reads")
MHVreads_graph

MHVpercentreads_graph <- final_table %>%
  ggplot(aes(x = cell , y = mhv_umi_reads_percent)) + 
  scale_fill_brewer(palette = 'Set1') + 
  geom_bar(aes(fill = time), stat = "identity", position = 'dodge') +
  theme_cowplot() + 
  facet_grid( ~ virus) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(x="MHV (+) RNA", y="Percent umi corrected reads")
MHVpercentreads_graph

```

### mRNA 

```{r}

mRNAreads_graph <- final_table %>%
  ggplot(aes(x = cell , y = mRNA_umi_reads)) + 
  scale_fill_brewer(palette = 'Set1') + 
  geom_bar(aes(fill = time), stat = "identity", position = 'dodge') +
  theme_cowplot() + 
  facet_grid( ~ virus) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(x="mRNA", y="Umi corrected reads")
mRNAreads_graph

mRNApercentreads_graph <- final_table %>%
  ggplot(aes(x = cell , y = mRNA_umi_reads_percent)) + 
  scale_fill_brewer(palette = 'Set1') + 
  geom_bar(aes(fill = time), stat = "identity", position = 'dodge') +
  theme_cowplot() + 
  facet_grid( ~ virus) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(x="mRNA", y="Percent umi corrected reads")
mRNApercentreads_graph


```

#18s rRNA

```{r}

r18sreads_graph <- final_table %>%
  ggplot(aes(x = cell , y = r18s_umi_reads)) + 
  scale_fill_brewer(palette = 'Set1') + 
  geom_bar(aes(fill = time), stat = "identity", position = 'dodge') +
  theme_cowplot() + 
  facet_grid( ~ virus) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(x="18s rRNA", y="Umi corrected reads")
r18sreads_graph

r18spercentreads_graph <- final_table %>%
  ggplot(aes(x = cell , y = r18s_umi_reads_percent)) + 
  scale_fill_brewer(palette = 'Set1') + 
  geom_bar(aes(fill = time), stat = "identity", position = 'dodge') +
  theme_cowplot() + 
  facet_grid( ~ virus) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(x="18s rRNA", y="Percent umi corrected reads")
r18spercentreads_graph

```

#5.8 rRNA

```{r}

r5.8sreads_graph <- final_table %>%
  ggplot(aes(x = cell , y = r5.8s_umi_reads)) + 
  scale_fill_brewer(palette = 'Set1') + 
  geom_bar(aes(fill = time), stat = "identity", position = 'dodge') +
  theme_cowplot() + 
  facet_grid( ~ virus) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(x="5.8s rRNA", y="Umi corrected reads")
r5.8sreads_graph

r5.8spercentreads_graph <- final_table %>%
  ggplot(aes(x = cell , y = r5.8s_umi_reads_percent)) + 
  scale_fill_brewer(palette = 'Set1') + 
  geom_bar(aes(fill = time), stat = "identity", position = 'dodge') +
  theme_cowplot() + 
  facet_grid( ~ virus) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(x="5.8s rRNA", y="Percent umi corrected reads")
r5.8spercentreads_graph

```

#5s

```{r}

r5sreads_graph <- final_table %>%
  ggplot(aes(x = cell , y = r5s_umi_reads)) + 
  scale_fill_brewer(palette = 'Set1') + 
  geom_bar(aes(fill = time), stat = "identity", position = 'dodge') +
  theme_cowplot() + 
  facet_grid( ~ virus) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(x="5s rRNA", y="Umi corrected reads")
r5sreads_graph

r5spercentreads_graph <- final_table %>%
  ggplot(aes(x = cell , y = r5s_umi_reads_percent)) + 
  scale_fill_brewer(palette = 'Set1') + 
  geom_bar(aes(fill = time), stat = "identity", position = 'dodge') +
  theme_cowplot() + 
  facet_grid( ~ virus) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(x="5s rRNA", y="Percent umi corrected reads")
r5spercentreads_graph

```

#28s rRNA

```{r}

r28sreads_graph <- final_table %>%
  ggplot(aes(x = cell , y = r28s_umi_reads)) + 
  scale_fill_brewer(palette = 'Set1') + 
  geom_bar(aes(fill = time), stat = "identity", position = 'dodge') +
  theme_cowplot() + 
  facet_grid( ~ virus) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(x="28s rRNA", y="Umi corrected reads")
r28sreads_graph

r28spercentreads_graph <- final_table %>%
  ggplot(aes(x = cell , y = r28s_umi_reads_percent)) + 
  scale_fill_brewer(palette = 'Set1') + 
  geom_bar(aes(fill = time), stat = "identity", position = 'dodge') +
  theme_cowplot() + 
  facet_grid( ~ virus) +
  theme(axis.text.x = element_text(angle = 60, hjust = 1)) +
  labs(x="28s rRNA", y="Percent umi corrected reads")
r28spercentreads_graph


```

##Graphs of percent total umi-reads for all RNA subtypes by cell type


###B6

```{r, warning = F}

B6_graph <- final_table %>%
        filter(cell == "B6") %>%
        gather(RNA_type, percent_total_reads, 11:16) %>%
        separate(RNA_type, into = c('RNA_type'), sep = '_') %>%
        ggplot(aes(x = RNA_type , y = percent_total_reads)) + 
        scale_fill_brewer(palette = 'Set1') + 
        geom_bar(aes(fill = time), stat = "identity", position = 'dodge') +
        theme_cowplot() + 
        facet_grid( ~ virus) +
        theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 8)) +
        labs(x="B6 WT macrophages", y="Percent umi corrected reads")
B6_graph
          

```

### RNaseL KO

```{r, warning = F}

RNaseL_graph <- final_table %>%
        filter(cell == "RNaseL") %>%
        gather(RNA_type, percent_total_reads, 11:16) %>%
        separate(RNA_type, into = c('RNA_type'), sep = '_') %>%
        ggplot(aes(x = RNA_type , y = percent_total_reads)) + 
        scale_fill_brewer(palette = 'Set1') + 
        geom_bar(aes(fill = time), stat = "identity", position = 'dodge') +
        theme_cowplot() + 
        facet_grid( ~ virus) +
        theme(axis.text.x = element_text(angle = 60, hjust = 1, size = 8)) +
        labs(x="B6 RNaseL KO macrophages", y="Percent umi corrected reads")
RNaseL_graph

```

